Rapid technological progress in white light-emitting diodes and its sources in innovation and technology spillovers

### 2023-05-29 2_SSL_NE/article/article_main.tex
added content to methods section

\hypersetup{
    pdftitle={Hybrid Life-Cycle Methods},
    pdfauthor={Michael Weinold, Guillaume Majeau-Bettez, Russell McKenna},
}

@@

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
\newline
$^1$ Technology Assessment Group, Paul Scherrer Institute, Switzerland \\
$^2$ ETH Zurich, Zurich, Switzerland \\
$^3$ CEENRG, Dept. of Land Economy, University of Cambridge, UK \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA

>>>>

\hypersetup{
    pdftitle={Hybrid Life-Cycle Methods},
    pdfauthor={Michael Weinold, Sergey Kolesnikov, Laura Diaz Anadon},
}

@@

M. Weinold$^{1,2,3}$, S. Kolesnikov$^3$, L.D. Anadon$^{3,4}$ \\
\newline
$^1$ CEENRG, Dept. of Land Economy, University of Cambridge, Cambridge,  UK \\
$^2$ ETH Zurich, Zurich, Switzerland \\
$^3$ Technology Assessment Group, Paul Scherrer Institute, Villigen, Switzerland \\
$^4$ Belfer Center for Science and International Affairs, Harvard University, Cambridge MA, USA
